---
title       : Motivation and pre-requisites
subtitle    : 
author      : Jeffrey Leek
job         : Johns Hopkins Bloomberg School of Public Health
logo        : bloomberg_shield.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow   # 
url:
  lib: ../librariesNew
  assets: ../assets
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---



```{r setoptions, cache = F, echo = F, message = F, warning = F, tidy = F}
library(knitr)
library(dplyr)
library(lattice)
# make this an external chunk that can be included in any file
options(width = 100)
#opts_chunk$set(message = F, error = F, warning = F, comment = NA, fig.align = 'center', dpi = 100, tidy = F)

options(xtable.type = 'html')
knit_hooks$set(inline = function(x) {
  if(is.numeric(x)) {
    round(x, getOption('digits'))
  } else {
    paste(as.character(x), collapse = ', ')
  }
})
#knit_hooks$set(plot = knitr:::hook_plot_html)
```


## About this course

* This course covers the basic ideas behind machine learning/prediction
  * Study design - training vs. test sets
  * Conceptual issues - out of sample error, ROC curves
  * Practical implementation - the caret package
* What this course depends on
  * The Data Scientist's Toolbox
  * R Programming
* What would be useful
  * Exploratory analysis
  * Reporting Data and Reproducible Research
  * Regression models

---




## Overview
The project is about


## Data Description
The data is come from the 

## Data Prepare Process
Preprocess the data


## predict the manner by machine learning
description the different method to predict


## Result
Give the result of 

## Expected out of sample error
Give the expected out of sample error


```{r}
summary(cars)
```

